---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(toxSummary)
```
App will run locally.  
## Workflow
app have two workflow. User can enter nonclinical data manually or user can pull 
nonclinical the data 
from database created from SEND data. Instruction for how to create SEND database can 
be found here [sendigR link].
whether user choose to enter data manually or pull from database for nonclinical part,
other part are same.

## Application Tab  
On the landing page (Application tab) there is a button  
on bottom of the left sidebar called "Need Help?".  
When user click on the button it will show how to use the app and
will provide self guided tour for all the button in this page.

## Edit Clinical Tab  
There is a button on top of the left column called "Need Help?".   
When user click on the button will provide self guided tour for all the button in this page.   

## Edit Nonclinical Tab    
There is a button on top of the left column called "Show Help Button". 
When user click on this button, it will show two other button 
1. Need Help? start here  
2. Manual Entry  
These button will provide self guided tour to this page and give information
what all input button does and how to enter data here.

## Plot   
When user create an application and add study information, app will create
plot and plot will be shown on Application Tab.   

## Table  
### Clinical Relevance Table  

### Key Findings Table  
### Safety Margin Table  